Properties of winning Iterated Prisoner's Dilemma strategies.

### 2020-03-27 paper/main.tex
finalises top performances section

This section evaluates the performance of \numberofstrategies IPD strategies. The performance of
each strategy is evaluated in four tournament types, which were presented in Section
\ref{section:data_collection}, followed by an evaluation of their performance
over all the \numberofalltournaments simulated tournaments of this work.

Each strategy participated in multiple tournaments of the same type (on average 5154).
For example Tit For Tat has participated in a total of 5114
tournaments of each type. The strategy's normalised rank distribution in these
is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A value of \(r =
0\) corresponds to a strategy winning the tournament where a value of
\(r = 1\) corresponds to the strategy coming last. Because of the strategies'
multiple entries their performance is evaluated based on the
\textbf{median normalised rank} denoted as \(\bar{r}\).

@@

The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
Table~\ref{table:top_performances}. The data collection process was design such
as that the probabilities of noise and ending of the match to vary between 0 and
1. However, commonly used values of these probabilities are
values less than 0.1. Thus,
Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
tournaments with \(p_n < 0.1\) and probabilistic ending tournaments with \(p_e <
0.1\).

\newcolumntype{g}{>{\columncolor{Gray}}l}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{\textwidth}{!}{
        \input{top_perfomances.tex}
    }
\end{center}
\caption{Top performances for each tournament type based on $\bar{r}$. The results
of each type are based on 11420 unique tournaments of each type. The results
for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments, and 
for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top ranks
indicate that trained strategies perform well in a variety of environments,
but so do simple deterministic strategies. The normalised medians are close to 0
for most environments, except environments with noise not restricted to 0.1.
These two tournaments have the highest medians, implying that strategies from
the collection of this work can not perform well in environments with such high
values of noise.}
\label{table:top_performances}
\end{table}

Distributions of these top ranked strategies are given by Figure~\ref{fig:r_distributions}.
\newpage

\begin{figure*}[!htbp]
    \centering
    \begin{subfigure}{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/performance_standard.pdf}
        \caption{$r$ distributions in standard tournaments.}\label{fig:std_results}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/noise_performance_subset.pdf}
        \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}{0.475\textwidth}
        \centering 
        \includegraphics[width=\textwidth]{../images/performance_noise.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_overall_results}
    \end{subfigure}
    \quad
    \begin{subfigure}{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/probend_performance_subset.pdf}
        \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
        tournaments with \(p_e < 0.1\).}
        \label{fig:probend_results}
    \end{subfigure}
    \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
    \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
    indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
\end{figure*}

In standard tournaments 10 out of the 15 top strategies are introduced
in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
hidden markov models (HMM), artificial neural networks (ANN), lookup tables
(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
reinforcement learning algorithms (evolutionary and particle swarm algorithms).
They have been trained to perform well against the strategies
in APL in a standard tournament, thus their performance in the
specific setting was anticipated. DoubleCrosser, BackStabber and Fool Me Once, are
strategies not from the literature but from the APL. DoubleCrosser is an extension
of BackStabber and both strategies make use of the number of turns because they are
set to defect on the last two rounds. It should be noted that these
strategies can be characterised as "cheaters". The source code of the strategies
allows them to known the number of turns in a match (if they are specified).
These strategies were expected to not perform as well in
tournaments where the number of turns is not specified. Finally, Winner
12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
DBS is a strategy specifically designed for noisy environments and it ranks
highly in standard tournaments as well.
Figure~\ref{fig:std_results} gives the distributions of $r$ for the top
ranked strategies. The distributions are skewed towards zero and the highest
median, of the top 15 strategies, is at 0.075. This indicates that the top ranked
strategies perform well in any given standard tournament, despite the opponents and
the number of turns.

In the case of noisy tournaments with \(p_n < 0.1\) the top performed strategies
include strategies specifically designed for noisy tournaments such as DBS,
Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
Omega Tit For Tat~\cite{kendall2007iterated}, strategies which performed well in
standard tournaments such as BackStabber, DoubleCrosser, Evolved ANN, FSM and
HMM and deterministic strategies such as Spiteful Tit For Tat~\cite{prison},
Level Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. The \(r\) distributions
of these strategies are given in Figure~\ref{fig:noise_results} where it is evident
that these strategies overall performed well in noisy tournaments.
In comparison, the top ranked strategies in noisy environments when \(p_n\in [0,
1]\) include strategies which decide their actions based on the cooperations to
defections ratio, such as ShortMem~\cite{Andre2013},
Grumpy~\cite{axelrodproject} and e~\cite{axelrodproject}, and the Retaliate
strategies which are designed to defect if the opponent has tricked them more
often than x\% of the times that they have done the same. The overall
performance of these strategies is bimodal,
Figure~\ref{fig:noise_overall_results}, indicating that although the top
ranked strategies mainly performed well, there are several tournaments that they
ranked in the bottom half. The bimodality of the \(r\) distributions can be
explained by Figure~\ref{fig:effect_of_noise} which gives the \(r\)
distributions for the top 6 strategies over the noise probability \(p_n\).
It is evident that the highly ranked strategies
were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
and that in tournaments with a noise probability lower than \(0.5\) they
performed poorly.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=\textwidth]{../images/noise_effect.pdf}
    \caption{\(r\) distributions for top 6 strategies in noisy tournaments over
    the probability of noisy ($p_n$).}
    \label{fig:effect_of_noise}
\end{figure}

In probabilistic ending tournaments with \(p_e < 0.1\) the effective strategies
are Meta strategies which include Nice Meta Winner, NMWE Finite Memory, NMWE
Deterministic, trained strategies which performed well in standard tournaments,
Grudger~\cite{axelrodproject} and Spiteful Tit for Tat~\cite{prison}. The Meta
strategies~\cite{axelrodproject} are a set of rules that create a team of
strategies and play as an ensemble or some other combination of their team
members. The distributions of the normalised rank in the 1139 probabilistic
ending tournaments with \(p_e < 0.1\), are shown in
Figure~\ref{fig:probend_results}. The medians of the top 15 strategies are lower
than 0.1 and the distributions are skewed towards 0. The strategies have overall
performed well in the probabilistic ending tournaments that they participated.

In probabilistic ending tournaments with \(p_e \in [0, 1]\) the top ranks are
mostly occupied by defecting strategies such as Better and Better, Gradual
Killer, Hard Prober (all from~\cite{axelrodproject}), Bully (Reverse Tit For
Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
state automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3,
Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
and Solution B1~\cite{Ashlock2014}. As stated in the Folk Theorem~\cite{Fudenberg2009}
defecting strategies do better when the likelihood of the game ending in the
next turn increased. This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
over \(p_e\). It  shows that the 6 strategies start of with a high median rank,
however, their ranked decreased as the the probability of the game ending
increased and at the point of \(p_e = 0.1\).

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=\textwidth]{../images/folk_theorem.pdf}
    \caption{\(r\) distributions for top 6 strategies in probabilistic ending tournaments
    over $p_e$.}
    \label{fig:effect_of_probend}
\end{figure}

In tournaments with both noise and an unspecified number of turns several of the
top ranked strategies are strategies that were highly ranked in noisy
tournaments. However, strategies from the top ranks in probabilistic ending
tournaments did not rank highly here.
The distributions of \(r\) shown in Figure~\ref{fig:noisy_probend_results} have
the largest median values compared to the top rank strategies of the other
tournament types. A subset of noisy probabilistic ending tournaments has been
considered such that \(p_e < 0.1\) and \(p_n < 0.1\). The top ranked strategies
are given in Table~\ref{table:subset_probend_noise_result} and it is shown that
the Meta strategies which performed well in noisy tournaments with \(p_n <
0.1\), perform well once again even the number of turns is not specified.
Moreover, several strategies that did well in probabilistic ending tournaments
such as Fortress 4, MEM2 and Spiteful Tit For Tat.

\begin{table}[!htbp]
    \centering
    \resizebox{.55\textwidth}{!}{
    \input{performance_probend_noise_subset_table.tex}}
    \caption{Top performances in 117 probabilistic ending tournaments with \(p_e < 0.1\) and \(p_n < 0.1\).}
    \label{table:subset_probend_noise_result}
\end{table}

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/performance_probend_noise.pdf}
        \caption{\(r\) distributions for best performed strategies in noisy
        probabilistic ending tournaments.}
        \label{fig:noisy_probend_results}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/performance_merged.pdf}
        \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.}
        \label{fig:overall_results}
    \end{subfigure}
    % \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
    % \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
    % indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
\end{figure}

This section presented the winning strategies in a series of IPD tournaments. In
standard tournaments the top spots were dominated by complex strategies that had
been trained using reinforcement learning techniques. In noisy environments where
the a noise probability strictly less than 0.1 was considered the successful
strategies were strategies based on the behaviour of many strategies and strategies
specifically designed for noisy tournaments. In
probabilistic ending tournaments most of the highly ranked strategies were defecting
strategies and trained finite state automata, all by the authors of~\cite{Ashlock2006, Ashlock2014}.
These strategies ranked high due to their performance in tournaments where the probability of the game ending after
each turn was bigger than 0.1. In probabilistic tournaments with \(p_e\) less than 0.1
the highly ranked strategies were trained and Meta strategies.
Finally the performance of all \numberofstrategies
strategies over the \numberofalltournaments tournaments in this manuscript was
assessed on \(\bar{r}\). The top ranked strategies were a mixture of behaviours
that did well in standard tournaments, tournaments with noise and a
few Meta strategies.
The results of this section imply that successful strategies for specific
settings exist for an IPD tournament. The top ranked strategies in both standard
tournaments and tournaments with probabilistic ending, managed to rank in the
top 10\% of the tournament most of the times.
Strategies in noisy
environments demonstrated that no strategy can be consistently
successful, expected if the value of noise is constrained to less than a 0.1.
Trained strategies, meta strategies and some deterministic defecting strategies
have demonstrated good performance over several tournament types, however,
there exists no one single strategy which appears to be dominant in an IPD
competition. The aim of the next section is to understand which are
the factors that made these strategies successful, in each setting separately
but also overall.

Be envious and be clever.

@@

\input{parameters_section}
% \input{overall_results}
\input{correlation_section}
\input{random_forest_evaluation}

>>>>

The performance of each strategy is evaluated in four tournament types, which
were presented in Section \ref{section:data_collection}, followed by an
evaluation of their performance over all the \numberofalltournaments simulated
tournaments of this work. Each strategy participated in multiple tournaments of
the same type (on average 5154). For example Tit For Tat has participated in a
total of 5114 tournaments of each type. The strategy's normalised rank
distribution in these is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A
value of \(r = 0\) corresponds to a strategy winning the tournament where a
value of \(r = 1\) corresponds to the strategy coming last. Because of the
strategies' multiple entries their performance is evaluated based on the
\textbf{median normalised rank} denoted as \(\bar{r}\).

@@

The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
Table~\ref{table:top_performances}. The data collection process was design such
as that the probabilities of noise and ending of the match varied between 0 and
1. However, commonly used values of these probabilities are
values less than 0.1. Thus,
Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
tournaments with \(p_n < 0.1\) and probabilistic ending tournaments with \(p_e <
0.1\).

\newcolumntype{g}{>{\columncolor{Gray}}l}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{\textwidth}{!}{
        \input{top_perfomances.tex}
    }
\end{center}
\caption{Top performances for each tournament type based on $\bar{r}$. The
results of each type are based on 11420 unique tournaments of each type. The
results for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments,
and for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top
ranks indicate that trained strategies perform well in a variety of
environments, but so do simple deterministic strategies. The normalised medians
are close to 0 for most environments, except environments with noise not
restricted to 0.1 regardless the number of turns. Noisy and noisy probabilistic
ending tournaments have the highest medians. This implies that strategies from
the collection of this work do not perform well in environments with high values
of noise.}
\label{table:top_performances}
\end{table}

The \(r\) distributions for the top ranked strategies of Table~\ref{table:top_performances}
are given by Figure~\ref{fig:r_distributions}.

\begin{figure*}[!htbp]
    \centering
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_standard.pdf}
        \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_noise_subset.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_subset_results}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}{0.485\textwidth}
        \centering 
        \includegraphics[width=\textwidth]{../images/r_distribution_noise.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_results}
    \end{subfigure}
    \quad
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_probend_subset.pdf}
        \caption{\(r\) distributions of top 15 strategies in 1139 probabilistic ending
        tournaments with \(p_e < 0.1\).}
        \label{fig:probend_subset_results}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}{0.485\textwidth}
        \centering 
        \includegraphics[width=\textwidth]{../images/r_distribution_probend.pdf}
        \caption{$r$ distributions of top 15 strategies in probabilistic ending tournaments.}\label{fig:probend_results}
    \end{subfigure}
    \quad
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_probend_noise.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy probabilistic ending tournaments.}
        \label{fig:probend_noise_results}
    \end{subfigure}
    \caption{\(r\) distributions of the top 15 strategies in different
    environments. A lower value of \(\bar{r}\) corresponds to a more successful
    performance. A strategy's \(r\) distribution skewed towards zero indicates
    that the strategy ranked highly in most tournaments it participated in. Most
    distributions are skewed towards zero except the distributions with
    unrestricted noise, supporting the conclusions from
    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
\end{figure*}

In standard tournaments 10 out of the 15 top strategies are introduced
in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
hidden markov models (HMM), artificial neural networks (ANN), lookup tables
(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
reinforcement learning algorithms (evolutionary and particle swarm algorithms).
They have been trained to perform well against the strategies
in APL in a standard tournament, thus their performance in the
specific setting was anticipated. DoubleCrosser, BackStabber and Fool Me Once, are
strategies not from the literature but from the APL. DoubleCrosser is an extension
of BackStabber and both strategies make use of the number of turns because they are
set to defect on the last two rounds. It should be noted that these
strategies can be characterised as "cheaters" because the source code of the strategies
allows them to known the number of turns in a match (if they are specified).
These strategies were expected to not perform as well in
tournaments where the number of turns is not specified. Finally, Winner
12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the literature.
DBS is a strategy specifically designed for noisy environments, however, it ranks
highly in standard tournaments as well.
Figure~\ref{fig:std_results} supports that these strategies are to perform
well in any standard tournament they participate.

In the case of noisy tournaments with \(p_n < 0.1\) the top performed strategies
include strategies specifically designed for noisy tournaments. These are DBS,
Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
Omega Tit For Tat~\cite{kendall2007iterated}. The rest of the top ranks are
occupied by strategies which performed well in standard tournaments and
deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. Similarly to standard
tournaments, the successful strategies in this given setting performed well
overall in the tournaments they participated in,
Figure~\ref{fig:noise_subset_results}.

In comparison, the performance the top ranked strategies in noisy environments
when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
decide their actions based on the cooperations to defections ratio, such as
ShortMem~\cite{Andre2013}, Grumpy~\cite{axelrodproject} and
e~\cite{axelrodproject}, and the Retaliate strategies which are designed to
defect if the opponent has tricked them more often than x\% of the times that
they have done the same. The bimodality of the \(r\) distributions is explained
by Figure~\ref{fig:effect_of_noise} which demonstrates that the top 6 strategies
were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
and that in tournaments with a noise probability lower than \(0.5\) they
performed poorly.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.92\textwidth]{../images/noise_effect.pdf}
    \caption{\(r\) distributions for top 6 strategies in noisy tournaments over
    the probability of noisy ($p_n$).}
    \label{fig:effect_of_noise}
\end{figure}

The most effective strategies in probabilistic ending tournaments with \(p_e
< 0.1\) are a series of Meta strategies, trained strategies which performed well
in standard tournaments, and  Grudger~\cite{axelrodproject} and Spiteful Tit for
Tat~\cite{prison}. he Meta strategies~\cite{axelrodproject} create a team of
strategies and play as an ensemble or some other combination of their team
members. Figure~\ref{fig:probend_subset_results} indicates that these strategies
performed well in any probabilistic ending tournament they competed in.

In probabilistic ending tournaments with \(p_e \in [0, 1]\) the top ranks are
mostly occupied by defecting strategies such as Better and Better, Gradual
Killer, Hard Prober (all from~\cite{axelrodproject}), Bully (Reverse Tit For
Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
state automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3,
Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
and Solution B1~\cite{Ashlock2014}. The success of defecting strategies in
probabilistic ending tournaments was excepted. As stated in the Folk
Theorem~\cite{Fudenberg2009} defecting strategies do better when the likelihood
of the game ending in the next turn increases.
This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
over \(p_e\).

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.92\textwidth]{../images/folk_theorem.pdf}
    \caption{\(r\) distributions for top 6 strategies in probabilistic ending tournaments
    over $p_e$. The 6 strategies start of with a high median rank,
    however, their ranked decreased as the the probability of the game ending
    increased and at the point of \(p_e = 0.1\).}
    \label{fig:effect_of_probend}
\end{figure}

The top performances in tournaments with both noise and a probabilistic ending
and the top performances over the entire data set have the largest median values
compared to the top rank strategies of the other tournament types,
Figure~\ref{fig:probend_noise_results} and Figure~\ref{fig:overall_results}. The
\(\bar{r}\) for the top strategy is approximately at 0.3, indicating that the
most successful strategy can on average just place at the top 30\% of the
competition.

\begin{table}[!htbp]
    \centering
    \resizebox{.30\textwidth}{!}{
    \input{performance_merged_table.tex}}
    \caption{Top performances over all the tournaments. The top ranks include
    strategies that have been previously mentioned. The set of Retaliate
    strategies occupy the top spots followed by BackStabber and DoubleCrosser.
    The distributions of the Retaliate strategies have no statistical
    difference. Thus, in an IPD tournament where the type is not specified,
    playing as any of the Retaliate strategies will have same the result. PSO
    Gambler and Evolved HMM 5 are trained strategies introduced
    in~\cite{Harper2017} and Nice Meta Winner and NMWE Memory One are strategies
    based on teams. Grudger is a strategy from Axelrod's original tournament and
    Forgetful Fool Me Once is based on the same approach as
    Grudger.}\label{table:overall_results}
\end{table}

\begin{figure}[!htbp]
        \centering
        \includegraphics[width=.65\textwidth]{../images/performance_merged.pdf}
        \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.
        A lower value of \(\bar{r}\) corresponds to a more successful
        performance.}
        \label{fig:overall_results}
\end{figure}

On the whole, the analysis of this manuscript has shown that:

\begin{itemize}
    \item In standard tournaments the dominating strategies were clever
    strategies that had been trained using reinforcement learning techniques.
    \item In noisy environments where the noise probability strictly less than
    0.1 was considered, the successful strategies were strategies specifically
    designed for noisy environments.
    \item In probabilistic ending tournaments most of the highly ranked
    strategies were defecting strategies and trained finite state automata, all
    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
    high due to their performance in tournaments where the probability of the
    game ending after each turn was bigger than 0.1.
    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
    ranked strategies were strategies based on the behaviour of others.
    \item From the collection of strategies considered here,  no strategy can be
    consistently successful in noisy environments, except if the value of noise
    is constrained to less than a 0.1.
\end{itemize}

Though there is not a single strategy that repeatably outranks all others in any
of the distinct tournament types, or even across the tournaments type, there
are specific types of strategies have been repeatably ranked in the top ranks.
These have been strategies that have been trained, strategies that defected
and strategies that would adapt their behaviour based on preassigned rules
to achieve the highest outcome. These results contradict Axelrod's suggestions,
and more specifically, the suggestions `Do not be clever' and `Do not be envious'.

@@

\input{parameters_section}
\input{correlation_section}
\input{random_forest_evaluation}
\input{strategies_list_section}

### 2020-03-27 paper/perfomances_table.tex
finalises top performances section

\begin{tabular}{lllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
1  &           Evolved FSM 16 &   0.00995 &                  \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
3  &  Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
4  &        PSO Gambler 2\_2\_2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
5  &              Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
6  &            Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
8  &            Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
9  &         PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
10 &                 Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
11 &             Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
12 &                      DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
13 &            DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
14 &              BackStabber &   0.07519 &                \$\textbackslash pi\$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lllllllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &                \$\textbackslash pi\$ &     0.317 \\
4  &        PSO Gambler 2\_2\_2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &      0.06 &     Anti Tit For Tat &     0.354 \\
6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
7  &        PSO Gambler 1\_1\_1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.407 \\
13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
\bottomrule
\end{tabular}
